### 2016-02-15 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Re-organized drawings in DelCo_2014_2015, edited struct. descr. in Hose/FDS reports

% Load packages
\usepackage{graphicx}
\usepackage[super]{nth}
\usepackage{placeins}
\usepackage{units}
\usepackage[percent]{overpic}

@@

\chapter{List of Symbols}
\begin{tabbing}
\hspace{1.5in} \= \\
ft \> foot \\
GPM \> gallons per minute \\
in. \> inch \\
m \> meter \\
\end{tabbing}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/hose_streams.pdf}
\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments. From left to right: straight stream, narrow fog stream, and wide fog stream.}
\label{fig:hose_streams}
\end{figure}
\FloatBarrier

@@

\subsection{Test Structures}
\label{subsec:test_structs}

\subsubsection{Construction}
\label{subsubsec:construction}
Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}. The structures were designed to simulate a single-story and a two-story residential structure. The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61 m (2 ft). The joints and gaps between the blocks were filled with high temperature insulation.

The interior walls of the first floor of each structure were framed with steel studs and track. The studs were set to 0.40 m (16 in.) centers. The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in.) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.13 in.) x 44 mm (1.75 in.) and an 11 mm (0.43 in.) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}. Tongue and grove, 18.3 mm (0.72 in.) thick, oriented strand board was screwed to the top of the TJIs.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/TJI_support}
\caption[TJI-constructed ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams. View is of the east side of the structure.}
\label{fig:TJI}
\end{figure}
\FloatBarrier

**** NEED TO GET SECOND STORY CONSTRUCTION DETAILS and then write a description of it here ****

The second floor of the West Structure was built on the wood floor assembly as described above. The walls were framed with wood studs set to 0.40 m (16 in.) centers.
% The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board. The ceiling of the burn room was the exposed "floor assembly". The walls of the hallway and entry foyer were composed of 16 mm (0.38 in) Type ****X**** gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/east_structure}
\\~\\
\includegraphics[width=6in]{../Pictures/west_structure}
\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
\label{fig:struct_pics}
\end{figure}

\subsubsection{Layout}
\label{subsubsec:layout}
The interior dimensions of each structure were approximately 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high. The exterior doorways of each structure and the stairwell doorway on the second level of the West Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure. All other doorways in the structures did not contain a door, so to close the doorway, a sheet of gypsum board was used to cover the opening and the doorway remained closed for the duration of the test procedure.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/East_Test_Structure_Dimensioned}
\caption[Plan view of the East Structure.]{East Structure floor layout.}
\label{fig:east_general_plan}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/West_Test_Structure_2nd_Floor_Dimensioned}
\\~\\
\includegraphics[width=6in]{../Drawings/West_Test_Structure_1st_Floor_Dimensioned}
\caption[Plan view of the second floor and first floor of the West Structure.]{Plan view of the second floor (top) and first floor (bottom) of the West Structure.}
\label{fig:west_general_plan}
\end{figure}

\subsection{Instrumentation}
\label{subsec:instrumentation}
A discussion of uncertainties for each type of measurement in this report can be found in Section~\ref{subsec:uncertainty}. For every experiment, gas velocity at an interior doorway was measured using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}. An array of 6 BDPs located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}. A single thermocouple was attached to each BDP to measure the temperature to be used in conjunction with the pressure measurement to derive velocity. Every thermocouple attached to the BDPs were exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in.) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in.) diameter Inconel shield that was 0.76 m (2.5 ft) in length.

The approximate locations of the BDPs used to measure air velocity are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup} and Figs.~\ref{fig:flow_path_1}-\ref{fig:flow_path_2}, respectively) found in Section~\ref{sec:exp_procedure}. To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by BDPs located at interior doorways are considered in this report. The set of BDPs at the northeast interior doorway of the East Structure, denoted as "A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80 m below the soffit of the doorway. The set of BDPs at the interior doorway in the West Structure, denoted as "A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.

\begin{figure}[!ht]
\includegraphics[width=3.5in]{../Pictures/BDPs_east}
\caption[Array of BDPs at interior doorway in East Structure.]{Array of BDPs located at the northeast interior doorway in the East Structure. View is looking at the array from Room C.}
\label{fig:BDPs}
\end{figure}
\FloatBarrier

\subsection{Uncertainty}
\label{subsec:uncertainty}
There are different components of uncertainty in the length, differential pressure, flow rate, and gas velocity reported here. Uncertainties are grouped into two categories according to the method used to estimate them. Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}. Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%. After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty. Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$). For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications. For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.

Each length measurement was taken carefully. Length measurements such as room dimensions,
instrumentation array locations, and nozzle placement were made with a hand-held laser measurement device which is has an accuracy of $\pm6.0$ mm (0.24 in.) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft)~\cite{Stanley}. However, conditions affecting the measurement, such as levelness of the device, yield an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range. Steel measuring tapes with a resolution of $\pm$0.5 mm were used to locate individual sensors within a measurement array and to measure and position the furniture. The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$ mm (0.06 in.) for 9.1 m (30 ft) tapes and $\pm6.4$ mm (0.25 in.) for 30.5 m (100 ft) tapes~\cite{NIST_Manual_44}. Some issues, such as "soft" edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.

@@

Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}. The meter consists of a section of 6.35 cm (2.5 in.) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate. The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\%  for the pressure sensor~\cite{Akron}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate. The total expanded uncertainty was estimated at $\pm10$\%.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/flow_meter}
\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\minipage{3in}
\begin{center}
	\includegraphics[width=2.9in]{../Pictures/monitor}
\end{center} 
\endminipage \hfill
\minipage{3in}
\begin{center}
	\includegraphics[width=2.9in]{../Pictures/handline}
\end{center}
\endminipage \hfill
\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75 in. handline (right) equipped with a combination nozzle and used to flow water during experiments.}
\label{fig:monitor+handline}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Hose_Test_Annotated}
\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A6 (blue square).}
\label{fig:east_setup}
\end{figure}

\begin{figure}[!ht]
\
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
\\~\\
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
\\~\\
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

\subsection{Monitor Experiments}
\label{subsec:monitor_procedure}
Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern. One test series, Test 33, occurred in the East Structure, and the two remaining series, Tests 16 and 17, occurred in the West Structure. Because monitor nozzles are designed to flow water from a set position, water was always applied in a fixed position during the monitor experiments. Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure.

@@

\begin{figure}[!ht]
\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/SS_Room_B_Test_33}
\\~\\
\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/NF_Room_B_Test_33}
\\~\\
\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/WF_Room_B_Test_33}
\caption[Straight stream, narrow fog stream, and wide fog stream during Test 33.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) pattern aimed at area above the doorway on the south wall of Room B during Test 33.}
\label{fig:test_33_pic}
\end{figure}

% Add flow chart? %
Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room. The nozzle was aimed at two targets during the series: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall. The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/SS_near}
\end{center} 
\endminipage \hfill
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/NF_near}
\end{center}
\endminipage \hfill
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/WF_near}
\end{center}
\endminipage \hfill
\vspace{0.15in}
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/SS_far}
\end{center} 
\endminipage \hfill
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/NF_far}
\end{center}
\endminipage \hfill
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/WF_far}
\end{center}
\endminipage \hfill
\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at "near" target (top row) and "far" target (bottom row) during the monitor experiments in the West Structure.}
\label{fig:test_16_17_pic}
\end{figure}
\FloatBarrier

\subsection{Handline Experiments}
\label{subsec:handline_procedure}
Numerous experiments were conducted during three different test series using a 1.75 in. handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern. One test series, Test 34, occurred in the East Structure, and the remaining series, Tests 18 and 19, occurred in the West Structure. All three test series primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.

Test 34 utilized a 1.75 in. handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}. The layout of the structure was identical to the layout described above in Section~\ref{subsec:monitor_procedure} and shown in Fig.~\ref{fig:east_setup}. The procedure for Test 34 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position. After 30 seconds, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the nozzle was aimed at the south doorway of Room B and water was applied for 30 seconds in a fixed position followed by 30 seconds in a clockwise pattern. This process was repeated for narrow fog and wide fog streams. Then, the entire procedure was repeated for the three types of streams being applied in the fixed and counter-clockwise pattern.

\begin{figure}[!ht]
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/SS_Room_B_Test_34}
\\~\\
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/NF_Room_B_Test_34}
\\~\\
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/WF_Room_B_Test_34}
\caption[Straight stream, narrow fog stream, and wide fog stream during Test 34.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test 34.}
\label{fig:test_34_pic}
\end{figure}

>>>>

% Load extra packages
\usepackage{placeins}

@@

% \chapter{List of Symbols}
% \begin{tabbing}
% \hspace{1.5in} \= \\
% ft \> foot \\
% GPM \> gallons per minute \\
% in \> inch \\
% m \> meter \\
% \end{tabbing}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/hose_streams.pdf}
	\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments. From left to right: straight stream, narrow fog stream, and wide fog stream.}
	\label{fig:hose_streams}
\end{figure}
\FloatBarrier

@@

\subsection{Test Structures}
\label{sec:test_structs}

\subsubsection{Construction}
\label{sec:construction}
Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}. The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure. The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft). The joints and gaps between the blocks were filled with high temperature insulation.

\begin{figure}[!ht]
	\includegraphics[width=5.25in]{../Figures/Pictures/east_structure}
	\\~\\
	\includegraphics[width=5.25in]{../Figures/Pictures/west_structure}
	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
	\label{fig:struct_pics}
\end{figure}

The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and \textit{were lined with 13~mm (0.5~in) thick cement board. The walls were composed of 16~mm (5/8~in) Type X gypsum board. Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.}
\FloatBarrier

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}. Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/TJI_support}
	\caption[TJI-constructed ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams. View is of the southeast corner of the structure.}
	\label{fig:TJI}
\end{figure}
\FloatBarrier

The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers. The interior walls were protected by 16~mm (5/8~in) fire rated gypsum board, 16~mm (5/8~in) durarock board, and a second layer of 16~mm (5/8~in) fire rated gypsum board. The exterior walls were protected with 11~mm (7/16~in) oriented strand board and 8~mm (5/16~in) fiber cement lap siding.

\subsubsection{Layout}
\label{sec:layout}
Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively. \textbf{Add N arrow to floor plans}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
	\label{fig:east_dimensioned_plan}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_dimensioned_plan}
\end{figure}

The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high. The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.

The exterior doorways of each structure and the stairwell doorway on the second level of the West Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure. All other doorways in the structures did not contain a door, so to close the doorway, a sheet of gypsum board was used to cover the opening and the doorway remained closed for the duration of the test procedure.
\FloatBarrier

\subsection{Instrumentation}
\label{sec:instrumentation}
A discussion of uncertainties for each type of measurement in this report can be found in Section~\ref{sec:uncertainty}. For every experiment, gas velocity at an interior doorway was measured using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}. An array of 6 BDPs located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}. A single thermocouple was attached to each BDP to measure the temperature to be used in conjunction with the pressure measurement to derive velocity. Every thermocouple attached to the BDPs were exposed-bead, Chromel-Alumel (type K) with a 1.0~mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2~mm (0.13 in) diameter Inconel shield that was 0.76~m (2.5~ft) in length.

The approximate locations of the BDPs used to measure air velocity are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup} and Figs.~\ref{fig:flow_path_1}-\ref{fig:flow_path_2}, respectively) found in Section~\ref{sec:exp_procedure}. To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by BDPs located at interior doorways are considered in this report. The set of BDPs at the northeast interior doorway of the East Structure, denoted as "A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80~m below the soffit of the doorway. The set of BDPs at the interior doorway in the West Structure, denoted as "A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95~m below the soffit of the corresponding doorway.

\begin{figure}[!ht]
	\includegraphics[width=3.5in]{../Figures/Pictures/BDPs_east}
	\caption[Array of BDPs at interior doorway in East Structure.]{Array of BDPs located at the northeast interior doorway in the East Structure. View is looking at the array from Room C.}
	\label{fig:BDPs}
\end{figure}
\FloatBarrier

\subsection{Uncertainty}
\label{sec:uncertainty}
There are different components of uncertainty in the length, differential pressure, flow rate, and gas velocity reported here. Uncertainties are grouped into two categories according to the method used to estimate them. Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}. Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%. After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty. Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$). For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications. For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.

Each length measurement was taken carefully. Length measurements such as room dimensions,
instrumentation array locations, and nozzle placement were made with a hand-held laser measurement device which is has an accuracy of $\pm6.0$~mm (0.24 in) over a range of 0.61~m (2.00~ft) to 15.3~m (50.0~ft)~\cite{Stanley}. However, conditions affecting the measurement, such as levelness of the device, yield an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range. Steel measuring tapes with a resolution of $\pm$0.5~mm were used to locate individual sensors within a measurement array and to measure and position the furniture. The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$~mm (0.06 in) for 9.1~m (30~ft) tapes and $\pm6.4$~mm (0.25 in) for 30.5~m (100~ft) tapes~\cite{NIST_Manual_44}. Some issues, such as "soft" edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.

@@

Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}. The meter consists of a section of 6.35 cm (2.5 in) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate. The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\%  for the pressure sensor~\cite{Akron}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate. The total expanded uncertainty was estimated at $\pm10$\%.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/flow_meter}
	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
	\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\minipage{3in}
	\begin{center}
		\includegraphics[width=2.9in]{../Figures/Pictures/monitor}
	\end{center} 
	\endminipage \hfill
	\minipage{3in}
	\begin{center}
		\includegraphics[width=2.9in]{../Figures/Pictures/handline}
	\end{center}
	\endminipage \hfill
	\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75 in handline (right) equipped with a combination nozzle and used to flow water during experiments.}
	\label{fig:monitor+handline}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
	\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A6 (blue square).}
	\label{fig:east_setup}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
	\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
	\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
	\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
	\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

\subsection{Monitor Experiments}
\label{sec:monitor_procedure}
Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern. One test series, Test 33, occurred in the East Structure, and the two remaining series, Tests 16 and 17, occurred in the West Structure. Because monitor nozzles are designed to flow water from a set position, water was always applied in a fixed position during the monitor experiments. Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure.

@@

\begin{figure}[!ht]
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/SS_Room_B_Test_33}
	\\~\\
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/NF_Room_B_Test_33}
	\\~\\
	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/WF_Room_B_Test_33}
	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 33.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) pattern aimed at area above the doorway on the south wall of Room B during Test 33.}
	\label{fig:test_33_pic}
\end{figure}

% Add flow chart? %
Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room. The nozzle was aimed at two targets during the series: a "near" target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a "far" target, located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_near}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_near}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_near}
	\end{center}
	\endminipage \hfill
	\vspace{0.15in}
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_far}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_far}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_far}
	\end{center}
	\endminipage \hfill
	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at "near" target (top row) and "far" target (bottom row) during the monitor experiments in the West Structure.}
	\label{fig:test_16_17_pic}
\end{figure}
\FloatBarrier

\subsection{Handline Experiments}
\label{sec:handline_procedure}
Numerous experiments were conducted during three different test series using a 1.75 in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern. One test series, Test 34, occurred in the East Structure, and the remaining series, Tests 18 and 19, occurred in the West Structure. All three test series primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.

Test 34 utilized a 1.75 in handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}. The layout of the structure was identical to the layout described above in Section~\ref{sec:monitor_procedure} and shown in Fig.~\ref{fig:east_setup}. The procedure for Test 34 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position. After 30 seconds, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the nozzle was aimed at the south doorway of Room B and water was applied for 30 seconds in a fixed position followed by 30 seconds in a clockwise pattern. This process was repeated for narrow fog and wide fog streams. Then, the entire procedure was repeated for the three types of streams being applied in the fixed and counter-clockwise pattern.

\begin{figure}[!ht]
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/SS_Room_B_Test_34}
	\\~\\
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/NF_Room_B_Test_34}
	\\~\\
	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/WF_Room_B_Test_34}
	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 34.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test 34.}
	\label{fig:test_34_pic}
\end{figure}
